---
title: "Homework 1"
author: "Lea Sauer, 23201699"
date: today
format:
  pdf:
    documentclass: report
    classoption: [twocolumn, landscape]
    toc: true #table of contents
    toc-title: '**Contents**'
    lof: true
editor: visual
execute: 
  eval: true
  echo: false
  message: false
  warning: false
  size: 15
---

## Dataset

The **BostonHousing2** data set from the 'mlbench' package contains 506 observations of 19 features from a census in Boston in the 1970. It contains some additional information to the orginal **BostonHousing** data set.

```{r}
#| label: dataset
#Load in the dataset from mlbench package 
data("BostonHousing2", package = "mlbench")
```

From the data set I am using the features

-medv: median value of owner-occupied homes in USD 1000's

-crim: per capita crime rate by town

## Visualisation

```{r}
#Load packages
library(ggplot2)
```

```{r}
#| label: plot
#| fig-width: 10
#| fig-height: 5
#| fig-cap: 'Crime rate vs House value on the Boston 1970 housing market'
#| warning: false

#Create plot 
ggplot(BostonHousing2, aes(x=medv,y=crim))+
  geom_point()+
  ggtitle('Crime rate vs House value')+
  labs(x='median value of owner-occupied homes in USD 1000s',y='per capita crime rate by town')+
  theme(plot.title = element_text( size=14, face="bold", hjust=0.5))+
geom_text(aes(13.5, 88.97620, label="Highest crime", color='red'))+ #label at point with highest crime rate
  theme(legend.position = "none")
  
```

In the figure we observe a lower crime rate the higher the housing value in Boston.
